---
title: "Replicate exhibits from the Second Edition of Meyers's Monograph"
output: html_document
---

[Meyers 2015]: http://www.casact.org/pubs/monographs/papers/01-Meyers.PDF
[Meyers 2016]: http://www.casact.org/pubs/forum/16wforum/Meyers.pdf
[Meyers 2019]: https://www.casact.org/pubs/monographs/papers/08-Meyers.pdf
[Meyers Case Study]: https://hubb.blob.core.windows.net/c7b64a78-dc16-47ec-91b4-31899c895f75-published/b1118727-dde3-4839-996e-9e7776cb3a65/AR-3%20-%20LL-Case-Study_CLRS.pdf?sv=2017-04-17&sr=c&sig=y%2FqwdCzUUbtRuGObrGrpGrB0YSjzwzwmzWbgCvgDdNM%3D&se=2021-12-26T17%3A55%3A01Z&sp=r

```{r setup, include=FALSE}
library(knitr)
library(locktonr)
library(tidyverse)
library(rstan)
library(loo)
library(ChainLadder)
library(parallel)
library(doParallel)
library(brms)
library(tidybayes)
library(flextable)
library(reservetestr)
library(patchwork)
library(bayesplot)

knitr::opts_chunk$set(
	fig.align = "center",
	fig.path = "figures/",
	message = FALSE,
	warning = FALSE,
	echo = FALSE
)

locktonr::gg_set_lockton_theme()

```

# Goal

Replicate results from the 2nd Edition of Glenn Meyers's Monograph [STOCHASTIC LOSS RESERVING USING BAYESIAN MCMC MODELS][Meyers 2019]. The focus is on the univariate results first. Loosely using R code provided by Meyers.

The package [reservetestr](https://github.com/problemofpoints/reservetestr) is used to access the data from the CAS loss reserve [database](http://www.casact.org/research/index.cfm?fa=loss_reserves_data) as well as additional helper functions. Meyers only uses a subset of the database. He chose four lines of business - comauto, ppauto, wkcomp, othliab - and selected 50 companies within each line. We can filter the full database to include only these companies.

```{r import-data}
triangle_data <- cas_loss_reserve_db %>% 
  get_meyers_subset(edition = 2)
```

Replicate Tables 2.1 to 2.3 from [Meyers (2019)][Meyers 2019].

```{r table_2.1}
illust_tri <- triangle_data %>% 
  filter(line == "comauto" & group_id == 353)
tibble(AY = 1:10, Premium = number_format(attr(illust_tri$train_tri_set[[1]]$paid, "exposure"))) %>% 
  pivot_wider(names_from = AY, values_from = Premium) %>% 
  regulartable() %>% 
  ft_lockton_theme() %>% 
  add_title_header("Table 2.1 Illustrative Loss Triangle Net Earned Premium")
```
```{r table_2.2}
illust_tri$full_long_tri[[1]] %>% 
  as.triangle(origin = "acc_yr", dev = "dev_lag", value = "cum_paid_loss") %>% 
  as.data.frame.matrix() %>% 
  rownames_to_column("AY \ Lag") %>% 
  as_tibble() %>% 
  mutate_at(-1, number_format) %>% 
  regulartable() %>% 
  ft_lockton_theme() %>% 
  add_title_header("Table 2.2 Paid Illustrative Loss Triangle Net of Reinsurance")
```

```{r table_2.3}
illust_tri$full_long_tri[[1]] %>% 
  as.triangle(origin = "acc_yr", dev = "dev_lag", value = "cum_caseinc_loss") %>% 
  as.data.frame.matrix() %>% 
  rownames_to_column("AY \ Lag") %>% 
  as_tibble() %>% 
  mutate_at(-1, number_format) %>% 
  regulartable() %>% 
  ft_lockton_theme() %>% 
  add_title_header("Table 2.3 Incurred Illustrative Loss Triangle Net of Reinsurance")
```

# 7. The Changing Settlement Rate Model

Run the Changing Settlement Rate (CSR) model. 

```{r run-csr-illustrative}

rstan_options(auto_write = TRUE)
options(mc.cores = parallel::detectCores())

stan_model_csr <- stan_model(file = here::here("stan/csr.stan"))

init_vals <- function(chain_id){

  set.seed(12345)
  
  list(r_alpha=rnorm(9,0,0.2),
       r_beta=runif(9),
       a_ig=runif(10),
       logelr=runif(1,-0.75,-0.5),
       gamma=rnorm(1,0,0.1))
  
}

illust_data_stan <- illust_tri$full_long_tri[[1]] %>% 
  filter((acc_yr + dev_lag - 1) <= 1997) %>% 
  select(acc_yr, dev_lag, cum_paid_loss, net_ep) %>% 
  transmute(origin_lag = acc_yr - min(acc_yr) + 1,
            dev_lag = dev_lag,
            logloss = log(cum_paid_loss),
            logprem = log(net_ep))

stan_data <- tidybayes::compose_data(illust_data_stan, 
                                     "n_dev" = max(illust_data_stan$dev_lag), 
                                     "n_origin" = max(illust_data_stan$origin_lag),
                                     .n_name = n_prefix("n_data"))

csr_fit <- sampling(stan_model_csr,
                    iter = 5000,
                    data = stan_data,
                    pars = c("r_alpha", "r_beta", "sig2"), include = FALSE,
                    init = init_vals, 
                    seed = 12345, 
                    control = list(adapt_delta = 0.999, max_treedepth = 50))
```

## Table 7.1

```{r table-7.1}
illust_csr_param_sims <- gather_draws(csr_fit, logelr, alpha[origin_lag], beta[origin_lag], gamma, sig[origin_lag])

illust_csr_param_sims %>% 
  summarise(.mean = mean(.value), .sd = sd(.value)) %>% 
  ungroup() %>% 
  mutate_at(3:4, number_format, 4) %>% 
  mutate(.variable = if_else(is.na(origin_lag), .variable, paste0(.variable, "_", origin_lag))) %>% 
  select(-origin_lag) %>% 
  regulartable() %>% 
  align(j=1, align = "left", part = "all") %>% 
  ft_lockton_theme() %>% 
  add_title_header("Table 7.1. CSR Model Parameter Summary - Paid")
```
## Figure 7.1

```{r figure-7.1}
illust_csr_param_sims %>% 
  filter(.variable == "gamma") %>% 
  ggplot(aes(x = .value)) +
  geom_histogram(color = lockton_colors$blue_gray) +
  geom_vline(xintercept = 0.0, color = lockton_colors$gold) +
  scale_x_continuous(breaks = c(-0.1, -0.05, 0, 0.05, 0.1, 0.15, 0.2)) +
  labs(x = "gamma", title = "Figure 7.1. CSR Posterior Distribution of gamma", 
       subtitle = "Paid Illustrative Loss Triangle")
```
```{r sim-predictions}
illust_sim_params <- spread_draws(csr_fit, logelr, alpha[origin_lag], 
                                      beta[dev_lag], speedup[dev_lag], sig[dev_lag]) %>% 
  ungroup() %>% 
  left_join(illust_data_stan %>% distinct(origin_lag, logprem), by = "origin_lag")

illust_sim_results <- illust_sim_params %>% 
  mutate(.value = rlnorm(nrow(illust_sim_params), logprem + logelr + alpha + beta * speedup, sig))
```

## Table 7.2 

```{r table-7.2}

illust_csr_pred_summary <- illust_sim_results %>%
  group_by(origin_lag, dev_lag) %>% 
  summarise(estimate = mean(.value),
            se = sd(.value), 
            cv = se / estimate) %>% 
  ungroup() %>% 
  bind_rows(
    illust_sim_results %>% 
      filter(dev_lag == 10) %>% 
      group_by(.draw) %>%
      summarise(.value = sum(.value)) %>% 
      summarise(estimate = mean(.value),
                se = sd(.value), 
                cv = se / estimate) %>% 
      add_column(origin_lag = NA, dev_lag = 10, .before = 1)
  )

illust_csr_pred_summary %>% 
  filter(dev_lag == 10) %>% 
  left_join(
    illust_tri$full_long_tri[[1]] %>% 
      filter(dev_lag == 10) %>% 
      mutate(origin_lag = acc_yr - min(acc_yr) + 1) %>% 
      select(origin_lag, cum_paid_loss, net_ep) %>% 
      add_row(origin_lag = NA, 
              cum_paid_loss = sum(.$cum_paid_loss), 
              net_ep = sum(.$net_ep)), by = "origin_lag") %>% 
  transmute("AY" = number_format(origin_lag), 
            "Premium" = number_format(net_ep), 
            "Estimate" = number_format(estimate),
            "SE" = number_format(se),
            "CV" = pct_format(cv),
            "Outcome" = number_format(cum_paid_loss)) %>% 
  regulartable() %>% 
  ft_lockton_theme() %>% 
  align(align = "right", part = "all") %>% 
  add_title_header("Table 7.2. CSR Model Output for the Paid Illustrative Loss Triangle")
```
## Posterior predictive distributions by accident year

```{r pp_check-csr}
illust_sim_results %>% 
  filter(.draw %in% which((.draw %% 100) == 1)) %>% 
  mutate(origin = origin_lag + 1988 - 1) %>% 
  ggplot() +
  geom_line(aes(x = dev_lag, y = .value, group = .draw), 
            alpha = 0.1, colour = lockton_colors$gray) +
  geom_line(aes(y = estimate, x = dev_lag), colour = lockton_colors$gold,
            data = illust_csr_pred_summary %>% 
              filter(!is.na(origin_lag)) %>% 
              mutate(origin = origin_lag + 1988 - 1)) +
  geom_point(aes(y = cum_paid_loss, x = dev_lag, fill = factor(obs)), 
             shape = 21, colour = lockton_colors$dark_blue,
             data = illust_tri$full_long_tri[[1]] %>% 
                      mutate(origin_lag = acc_yr - min(acc_yr) + 1,
                             origin = acc_yr,
                             obs = if_else(dev_yr <= max(acc_yr), "Observation", "Hold out"))) +
  scale_fill_manual(values = c("white", lockton_colors$dark_blue)) +
  facet_wrap(~ origin) +
  scale_y_continuous(labels = scales::number_format(big.mark = ",")) +
  scale_x_continuous(breaks = seq(from = 2, to = 10, by = 2)) +
  labs(x = "Development year", y = "Cumulative Paid Loss ($)",
       title = "Illustrative Insurer - Posterior predictive check",
       subtitle = "Cumulative paid losses")
```

## Figure 7.3

```{r figure-7.3}
fitted_vals <- spread_draws(csr_fit, mu[n_data]) %>% 
  ungroup() %>% 
  filter(.draw <= 100) %>% 
  left_join(illust_data_stan %>% 
              mutate(n_data = 1:n()), by = "n_data") %>% 
  left_join(spread_draws(csr_fit, sig[dev_lag]) %>% 
              ungroup() %>% 
              select(.draw, dev_lag, sig), by = c(".draw","dev_lag")) %>% 
  mutate(.std_resid = (logloss - mu) / sig,
         cal_yr = origin_lag + dev_lag - 1)

## ---- resid_ggplot ----
gg_resid_plot <- function(df, x_var, x_lab = NULL, y_lab = NULL){
  
  gg <- ggplot(data = df, aes_string(y = ".std_resid")) +
    geom_hline(aes(yintercept = 0), size=0.65) +
    geom_hline(aes(yintercept = -3), size=0.65) +
    geom_hline(aes(yintercept = 3), size=0.65) +
    geom_point(aes_string(x = x_var)) +
    ylim(-4.0, 4.0) + scale_x_continuous(breaks = c(2,4,6,8,10)) +
    xlab(x_lab) + ylab(y_lab) +
    ggtitle(paste0(x_lab,""))
  
  gg
  
}
gg_resid_boxplot <- function(df, x_var, x_lab = NULL, y_lab = NULL){
  
  gg <- ggplot(data = df, aes_string(y = ".std_resid")) +
    geom_hline(aes(yintercept = 0), size=0.65) +
    geom_hline(aes(yintercept = -0.675), size=0.65) +
    geom_hline(aes(yintercept = 0.675), size=0.65) +
    geom_boxplot(aes_string(x = x_var, group = x_var), colour = lockton_colors$gold) +
    scale_x_continuous(breaks = c(2,4,6,8,10)) +
    scale_y_continuous(breaks = c(-3:3), limits = c(-3,3)) +
    xlab(x_lab) + ylab(y_lab) +
    ggtitle(paste0(x_lab,""))
  
  gg
  
}

gg_resid_boxplot(fitted_vals, "origin_lag", x_lab = "Accident year", y_lab = "Standardized residuals") +
gg_resid_boxplot(fitted_vals, "dev_lag", x_lab = "Development year") +
gg_resid_boxplot(fitted_vals, "cal_yr", x_lab = "Calendar year", y_lab = "Standardized residuals") + 
  patchwork::plot_layout(nrow = 2)
```

## Optimize current CSR Stan code

- add alternative speedup formulations

```{r run-csr-illustrative2, message=FALSE, warning=FALSE}

stan_model_csr2 <- stan_model(file = here::here("stan/csr2.stan"))

stan_data2_prior <- c(stan_data, 
                    list(prior_only = TRUE,
                     logelrparams = c(-0.4, 0.7),
                     alphasigma = 0.5,
                     betaparams = matrix(c(-log(rev(1/summary(MackChainLadder(illust_tri$train_tri_set[[1]]$paid))$ByOrigin$Dev.To.Date)), 
                                           rep(0.5, 10)), 
                                         ncol = 2, nrow = 10),
                     sigparams = 0.2,
                     gammasig = 0.15))

stan_data2 <- c(stan_data, 
                list(prior_only = FALSE,
                     logelrparams = c(-0.4, 1),
                     alphasigma = 2,
                     betaparams = matrix(c(rep(0, 10), rep(2, 10)), 
                                         ncol = 2, nrow = 10),
                     sigparams = 0.8,
                     gammasig = 0.1))

csr_fit2 <- sampling(stan_model_csr2,
                    iter = 5000,
                    data = stan_data2,
                    pars = c("r_alpha", "r_beta"), include = FALSE,
                    init = init_vals, 
                    seed = 12345, 
                    control = list(adapt_delta = 0.999, max_treedepth = 50))

csr_fit2_map <- vb(stan_model_csr2,
                   data = stan_data2,
                   pars = c("r_alpha", "r_beta"), include = FALSE,
                   init = init_vals,
                   seed = 12345)
```

```{r csr-investigate-priors}

csr_fit2_prior <- sampling(stan_model_csr2,
                    iter = 2000,
                    data = stan_data2_prior,
                    pars = c("r_alpha", "r_beta"), include = FALSE,
                    init = init_vals, 
                    seed = 12345, 
                    control = list(adapt_delta = 0.999, max_treedepth = 50))

illust_csr_param_sims_prior <- gather_draws(csr_fit2, logelr, alpha[origin_lag], beta[origin_lag], gamma, sig[origin_lag])

illust_csr_param_sims_prior %>% 
  summarise(.mean = mean(.value), .sd = sd(.value)) %>% 
  ungroup() %>% 
  mutate_at(3:4, number_format, 4) %>% 
  mutate(.variable = if_else(is.na(origin_lag), .variable, paste0(.variable, "_", origin_lag))) %>% 
  select(-origin_lag) %>% 
  regulartable() %>% 
  align(j=1, align = "left", part = "all") %>% 
  ft_lockton_theme() %>% 
  add_title_header("Table 7.1. CSR Model Parameter Summary - Paid")
```

```{r prior-dist}
mcmc_areas(
   as.array(csr_fit2), 
   pars = vars("logelr", "gamma", 
               contains("sig"), contains("alpha"), contains("beta")),
   prob = 0.8, # 80% intervals
   prob_outer = 0.99, # 99%
   point_est = "mean") + 
  ggplot2::labs(
    title = "Prior parameter distributions",
    subtitle = "with medians and 80% intervals")

illust_csr_param_sims_prior %>% ungroup() %>% filter(.variable=="logelr") %>% 
  mutate(.value = exp(.value)) %>% pull(.value) %>% qplot()
illust_csr_param_sims_prior %>% ungroup() %>% filter(.variable=="gamma") %>% 
  pull(.value) %>% qplot()
illust_csr_param_sims_prior %>% ungroup() %>% 
  filter(.variable=="alpha" & origin_lag != 1) %>% 
  mutate(.value = exp(.value)) %>%
  ggplot(aes(x=.value)) + 
  geom_histogram() + 
  facet_wrap(~ origin_lag)
illust_csr_param_sims_prior %>% ungroup() %>% 
  filter(.variable=="beta" & origin_lag != 10) %>% 
  mutate(.value = exp(.value)) %>%
  ggplot(aes(x=.value)) + 
  geom_histogram() + 
  facet_wrap(~ origin_lag)
illust_csr_param_sims_prior %>% ungroup() %>% 
  filter(.variable=="sig") %>% 
  ggplot(aes(x=.value)) + 
  geom_histogram() + 
  facet_wrap(~ origin_lag)
```


```{r ppc-sims}
illust_sim_params_prior <- spread_draws(csr_fit2, logelr, alpha[origin_lag], 
                                      beta[dev_lag], speedup[dev_lag], sig[dev_lag]) %>% 
  ungroup() %>% 
  left_join(illust_data_stan %>% distinct(origin_lag, logprem), by = "origin_lag")

illust_sim_results_prior <- illust_sim_params_prior %>% 
  mutate(.value = rlnorm(nrow(illust_sim_params_prior), logprem + logelr + alpha + beta * speedup, sig))

illust_csr_pred_summary_prior <- illust_sim_results_prior %>%
  group_by(origin_lag, dev_lag) %>% 
  summarise(estimate = mean(.value),
            se = sd(.value), 
            cv = se / estimate) %>% 
  ungroup() %>% 
  bind_rows(
    illust_sim_results_prior %>% 
      filter(dev_lag == 10) %>% 
      group_by(.draw) %>%
      summarise(.value = sum(.value)) %>% 
      summarise(estimate = mean(.value),
                se = sd(.value), 
                cv = se / estimate) %>% 
      add_column(origin_lag = NA, dev_lag = 10, .before = 1)
  )

illust_csr_pred_summary_prior %>% 
  filter(dev_lag == 10) %>% 
  left_join(
    illust_tri$full_long_tri[[1]] %>% 
      filter(dev_lag == 10) %>% 
      mutate(origin_lag = acc_yr - min(acc_yr) + 1) %>% 
      select(origin_lag, cum_paid_loss, net_ep) %>% 
      add_row(origin_lag = NA, 
              cum_paid_loss = sum(.$cum_paid_loss), 
              net_ep = sum(.$net_ep)), by = "origin_lag") %>% 
  transmute("AY" = number_format(origin_lag), 
            "Premium" = number_format(net_ep), 
            "Estimate" = number_format(estimate),
            "SE" = number_format(se),
            "CV" = pct_format(cv),
            "Outcome" = number_format(cum_paid_loss)) %>% 
  regulartable() %>% 
  ft_lockton_theme() %>% 
  align(align = "right", part = "all") %>% 
  add_title_header("Table 7.2. CSR Model Output for the Paid Illustrative Loss Triangle")

```

```{r pp_check-csr-priors}
illust_sim_results_prior %>% 
  filter(.draw %in% which((.draw %% 100) == 1)) %>% 
  mutate(origin = origin_lag + 1988 - 1) %>% 
  ggplot() +
  geom_line(aes(x = dev_lag, y = .value, group = .draw), 
            alpha = 0.1, colour = lockton_colors$gray) +
  geom_line(aes(y = estimate, x = dev_lag), colour = lockton_colors$gold,
            data = illust_csr_pred_summary_prior %>% 
              filter(!is.na(origin_lag)) %>% 
              mutate(origin = origin_lag + 1988 - 1)) +
  geom_point(aes(y = cum_paid_loss, x = dev_lag, fill = factor(obs)), 
             shape = 21, colour = lockton_colors$dark_blue,
             data = illust_tri$full_long_tri[[1]] %>% 
                      mutate(origin_lag = acc_yr - min(acc_yr) + 1,
                             origin = acc_yr,
                             obs = if_else(dev_yr <= max(acc_yr), "Observation", "Hold out"))) +
  scale_fill_manual(values = c("white", lockton_colors$dark_blue)) +
  facet_wrap(~ origin) +
  scale_y_continuous(labels = scales::number_format(big.mark = ",")) +
  scale_x_continuous(breaks = seq(from = 2, to = 10, by = 2)) +
  labs(x = "Development year", y = "Cumulative Paid Loss ($)",
       title = "Illustrative Insurer - Prior predictive check",
       subtitle = "Cumulative paid losses")
```

```{r brms}
csr_brms <- brm(bf(logloss ~ 1 + offset(logprem) + (1 | origin_lag) + dev_lag),
                data = illust_data_stan %>% mutate(dev_lag = as.factor(dev_lag)),
                family = gaussian(), 
                save_model = here::here("stan/csr_brms2.stan"))

```

# Run CSR method on 200 paid loss triangles

- add hierarchical component (alphas)
- test mick enhanced Clark/Guzsca model
- test hierarchical component model











