---
title: "Replicate exhibits from the Second Edition of Meyers's Monograph"
output: html_document
---

[Meyers 2015]: http://www.casact.org/pubs/monographs/papers/01-Meyers.PDF
[Meyers 2016]: http://www.casact.org/pubs/forum/16wforum/Meyers.pdf
[Meyers 2019]: https://www.casact.org/pubs/monographs/papers/08-Meyers.pdf
[Meyers Case Study]: https://hubb.blob.core.windows.net/c7b64a78-dc16-47ec-91b4-31899c895f75-published/b1118727-dde3-4839-996e-9e7776cb3a65/AR-3%20-%20LL-Case-Study_CLRS.pdf?sv=2017-04-17&sr=c&sig=y%2FqwdCzUUbtRuGObrGrpGrB0YSjzwzwmzWbgCvgDdNM%3D&se=2021-12-26T17%3A55%3A01Z&sp=r

```{r setup, include=FALSE}
library(knitr)
library(locktonr)
library(tidyverse)
library(rstan)
library(loo)
library(ChainLadder)
library(parallel)
library(doParallel)
library(brms)
library(tidybayes)
library(flextable)
library(reservetestr)

knitr::opts_chunk$set(
	fig.align = "center",
	fig.path = "figures/",
	message = FALSE,
	warning = FALSE,
	echo = FALSE
)

locktonr::gg_set_lockton_theme()

```

# Goal

Replicate results from the 2nd Edition of Glenn Meyers's Monograph [STOCHASTIC LOSS RESERVING USING BAYESIAN MCMC MODELS][Meyers 2019]. The focus is on the univariate results first. Loosely using R code provided by Meyers.

The package [reservetestr](https://github.com/problemofpoints/reservetestr) is used to access the data from the CAS loss reserve [database](http://www.casact.org/research/index.cfm?fa=loss_reserves_data) as well as additional helper functions. Meyers only uses a subset of the database. He chose four lines of business - comauto, ppauto, wkcomp, othliab - and selected 50 companies within each line. We can filter the full database to include only these companies.

```{r import-data}
triangle_data <- cas_loss_reserve_db %>% 
  get_meyers_subset(edition = 2)
```

Replicate Tables 2.1 to 2.3 from [Meyers (2019)][Meyers 2019].

```{r table_2.1}
illust_tri <- triangle_data %>% 
  filter(line == "comauto" & group_id == 353)
tibble(AY = 1:10, Premium = number_format(attr(illust_tri$train_tri_set[[1]]$paid, "exposure"))) %>% 
  pivot_wider(names_from = AY, values_from = Premium) %>% 
  regulartable() %>% 
  ft_lockton_theme() %>% 
  add_title_header("Table 2.1 Illustrative Loss Triangle Net Earned Premium")
```
```{r table_2.2}
illust_tri$full_long_tri[[1]] %>% 
  as.triangle(origin = "acc_yr", dev = "dev_lag", value = "cum_paid_loss") %>% 
  as.data.frame.matrix() %>% 
  rownames_to_column("AY \ Lag") %>% 
  as_tibble() %>% 
  mutate_at(-1, number_format) %>% 
  regulartable() %>% 
  ft_lockton_theme() %>% 
  add_title_header("Table 2.2 Paid Illustrative Loss Triangle Net of Reinsurance")
```

```{r table_2.3}
illust_tri$full_long_tri[[1]] %>% 
  as.triangle(origin = "acc_yr", dev = "dev_lag", value = "cum_caseinc_loss") %>% 
  as.data.frame.matrix() %>% 
  rownames_to_column("AY \ Lag") %>% 
  as_tibble() %>% 
  mutate_at(-1, number_format) %>% 
  regulartable() %>% 
  ft_lockton_theme() %>% 
  add_title_header("Table 2.3 Incurred Illustrative Loss Triangle Net of Reinsurance")
```

# 7. The Changing Settlement Rate Model

Run the Changing Settlement Rate (CSR) model. 

```{r run-csr-illustrative}

options(mc.cores = parallel::detectCores())

stan_model_csr <- stan_model(file = here::here("stan/csr.stan"))

init_vals <- function(chain_id){

  set.seed(12345)
  
  list(r_alpha=rnorm(9,0,0.2),
       r_beta=runif(9),
       a_ig=runif(10),
       logelr=runif(1,-0.75,-0.5),
       gamma=rnorm(1,0,0.1))
  
}

illust_data_stan <- illust_tri$full_long_tri[[1]] %>% 
  filter((acc_yr + dev_lag - 1) <= 1997) %>% 
  select(acc_yr, dev_lag, cum_paid_loss, net_ep) %>% 
  transmute(origin_lag = acc_yr - min(acc_yr) + 1,
            dev_lag = dev_lag,
            logloss = log(cum_paid_loss),
            logprem = log(net_ep))

stan_data <- tidybayes::compose_data(illust_data_stan, 
                                     "n_dev" = max(illust_data_stan$dev_lag), 
                                     "n_origin" = max(illust_data_stan$origin_lag),
                                     .n_name = n_prefix("n_data"))

csr_fit <- sampling(stan_model_csr, 
                    data = stan_data,
                    pars = c("r_alpha", "r_beta", "sig2"), include = FALSE,
                    init = init_vals, 
                    seed = 12345, 
                    control = list(adapt_delta = 0.999, max_treedepth = 50))
```

```{r csr-illustrative-params}
csr_fit
```






















